---
title: "2021-12-28 Recent Tactics OTB"
layout: post
always_allow_html: yes
output:
  md_document:
    variant: gfm
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rchess)
library(ggambit)


```


I managed to find a nice tactic in my OTB game in November 21 to finish. Here  white played  29. Nd6 forking my rooks.

I had seen the fork but wasn't worried. My main concern was that my car was in a multistorey car park that closed at 10.30 it was now 9:50 and I thought I didnt have time for an ending I needed to find a finish -so I
stared at the board thinking something must be there and there was.

```{r board,echo = FALSE}

fen <- "2r1r1k1/5ppp/8/1N1p4/8/1PP5/2KQN1PP/q7 w - - 0 29"
plot_fen(fen, perspective = "b",
  palette = "brown",
  piece_scale = 0.95,
  show_coords = TRUE,
  show_fen = FALSE,
  news_spacing = 0.15,
  news_thickness = 0.2,
  border_col = NA,
  border_size = 0.50) 
```

## Solution

<div id="spoiler" style="display:none">
29 Nd6? Rxe2 (my opponent resigned here)  as 30. Qxe2 Rxc3+ 31. Kd2 Qc1#  or is losing the queen 
</div>

<button title="Click to show answer" type="button"
   onclick="if(document.getElementById('spoiler') .style.display=='none')
              {document.getElementById('spoiler') .style.display=''}
            else{document.getElementById('spoiler') .style.display='none'}">
  Show/hide
</button>

